IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/retrofit.tex
wip

>>>>

Existing language-based coarse-grained IFC
system~\cite{Hritcu:2013:YIB:2497621.2498098,stefan:2012:arxiv-flexible} allow
a sub-computation to temporarily raise the floating-label; after its
completion, the floating-label is restore to its original label. When this
occurs, the enforcement must ensure, through several IFC checks, that information
does not leak to the (less confidential) program continuation. The presence of
exceptions clearly adds intricacies to the enforcement.
